\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
    linkcolor = red,
    urlcolor  = blue,
    citecolor = blue,
    anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\newfontfamily{\SansTC}[
    Path = Fonts/NotoSansTC/,
    Extension = .ttf,
    BoldFont = NotoSansTC-Bold,
]{NotoSansTC-Regular}

\newfontfamily{\SerifTC}[
    Path = Fonts/NotoSerifTC/,
    Extension = .ttf,
    BoldFont = NotoSerifTC-Bold,
]{NotoSerifTC-Regular}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\classesList}[4]{
    \item\small{
            {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
{\Huge Yu-Wei Tseng}
\\ \vspace{0pt}
\small
\raisebox{-0.1\height}\faPhone\ +1 469-268-5457 ~
\href{mailto:dadavidtseng@gmail.com}{\faEnvelope\ dadavidtseng@gmail.com} ~
\href{https://linkedin.com/in/dadavidtseng}{\faLinkedin\ dadavidtseng}  ~
\href{https://github.com/dadavidtseng}{\faGithub\ dadavidtseng}
\vspace{-6pt}
\end{center}

% adjust vscape based on the space you want to leave between each section.

%-----------Technical Skills-----------


\section{Skills}
\textbf{Programming Languages}{: C, C++, C\#, Python, Go, TypeScript, SQL, LaTeX} \\
\textbf{AI \& Frameworks}{: LLM Integration (Claude), MCP, Agentic Orchestration, Behavior Trees} \\
\textbf{Web \& Infrastructure}{: React, Node.js, Express, WebSocket, ArcadeDB, Docker, Git, Perforce} \\
\textbf{Game \& Graphics}{: Unreal Engine 5, Unity, DirectX 11, HLSL, FMOD, Blender} \\
\textbf{Methodologies}{: Agile/Scrum, Object-Oriented Design, Design Patterns, ECS Architecture}\\

%\textbf{Languages}{: Taiwanese Mandarin (native), English (fluent, TOEIC 895, TOEFL 105, GRE 315), French (beginner)}

%-----------PROJECTS-----------

\section{Projects}
\vspace{-8pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/projects/daemon-engine}{Daemon Engine}} $|$ \emph{C++, DirectX11, V8 JavaScript Engine} $|$ \href{https://github.com/dadavidtseng/DaemonEngine}{Git}}{August 2024 -- Present}
\resumeItemListStart
\resumeItem{Developed a custom game engine with a DirectX 11 rendering pipeline supporting 2D and 3D rendering.}
\resumeItem{Created custom math and physics utilities including vectors, Euler angles and matrices for collisions and raycasts.}
\resumeItem{Embedded V8 JavaScript runtime enabling hot-reloadable gameplay scripting with Chrome DevTools debugging.}
\resumeItem{Implemented multithreaded JobSystem with generic and I/O worker pools using bitfield-based task claiming.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/projects/agents}{AGENTS}} $|$ \emph{C++, JavaScript, TypeScript, Python, Rust, Go, MCP, React, Astro} $|$ \href{https://github.com/dadavidtseng/AGENTS}{Git}}{July 2025 -- Present}
\resumeItemListStart
\resumeItem{Architected a distributed multi-agent orchestration platform with quest-based task decomposition, parallel execution via git worktree isolation, and human-in-the-loop approval gates.}
\resumeItem{Built orchestration layer (agent-producer) that breaks high-level goals into executable tasks, assigns to specialized agents, and verifies completion using LLM-based evaluation.}
\resumeItem{Implemented dual-layer memory: short-term (local JSON) and long-term (ArcadeDB graph database) for persistent agent context, task dependencies, and relationship tracking.}
\resumeItem{Developed 34-tool MCP server for quest/task management, shadow agent monitoring with automatic rollback, and cross-language message routing across C++, TypeScript, Python, Rust, and Go.}
\resumeItem{Built React + Express real-time dashboard with WebSocket updates, and integrated Slack/Discord bots for notification pipelines.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/projects/daemon-windows}{DaemonWindows}} $|$ \emph{Daemon Engine} $|$ \href{https://github.com/dadavidtseng/DaemonWindows}{Git}}{May 2025 -- Present}
\resumeItemListStart
\resumeItem{Built multi-window action game using Win32 API with runtime-adjustable window instances as game objects.}
\resumeItem{Implemented wave-based survival gameplay with shop upgrade system and boss encounters.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{\href{https://dadavidtseng.info/projects/daemon-chess}{DaemonChess}} $|$ \emph{Daemon Engine} $|$ \href{https://github.com/dadavidtseng/DaemonChess}{Git}}{May 2025 -- July 2025}
\resumeItemListStart
\resumeItem{Developed networked 3D chess with TCP WebSocket client-server architecture.}
\resumeItem{Implemented complete chess rule engine (en passant, castling, promotion) with Blinn-Phong shading and raycast interaction.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8pt}
%-----------EXPERIENCE-----------

\section{Experiences}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.smu.edu/guildhall}
{Game AI Engineer}
    $($\href{https://www.smu.edu/guildhall}{Corrupted Hollow}$)$}
{May 2025 -- January 2026}
{SMU Guildhall $|$ Unreal Engine 5.7 $|$ Team of 24 $|$ \href{https://store.steampowered.com/app/3533890/HardDriverz/?curator_clanid=34088398}{Steam}}{Dallas, TX}
\resumeItemListStart
\resumeItem{Established module-based architecture and coding standards for a 24-person cross-discipline team.}
\resumeItem{Researched and designed behavior tree-based AI system with Unreal Engine's MassEntity system and StateTree.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.smu.edu/guildhall}
{Game UI Engineer}
    $($\href{https://www.smu.edu/guildhall}{HardDriverz}$)$}
{February 2025 -- May 2025}
{SMU Guildhall $|$ Unreal Engine 5.6 $|$ Team of 53 $|$ \href{https://store.steampowered.com/app/3533890/HardDriverz/?curator_clanid=34088398}{Steam}}{Dallas, TX}
\resumeItemListStart
\resumeItem{Implemented out-of-game UI per designer specifications using UMG-based menu framework with network-replicated lobby.}
\resumeItem{Collaborated with two programmers, an artist, and a designer to integrate car selection menu flow.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.smu.edu/guildhall}
{Gameplay Engineer}
    $($\href{https://www.smu.edu/guildhall}{PlanePainter}$)$}
{August 2024 -- January 2025}
{SMU Guildhall $|$ Unity $|$ Team of 5 $|$ \href{https://store.steampowered.com/app/3533890/HardDriverz/?curator_clanid=34088398}{Steam}}{Dallas, TX}
\resumeItemListStart
\resumeItem{Provided a configurable level parameters to level designers using Unity's ScriptableObject.}
\resumeItem{Advised artists for a better layered and organized UI and In-Game art assets and implemented the logic }
\resumeItem{Collaborated two artists and two designers to establish the game’s mechanics and design goals.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.ctrls1890.com/}
{Junior Software Engineer}}
{November 2023 -- June 2024}
{CtrlS Ltd. $|$ Unity}
{Tainan, Taiwan}
\resumeItemListStart
\resumeItem{Developed 360-degree AR streaming video application on Android mobile devices.}
\resumeItem{Built serious games for Android with integrated touchpad and digital pen drawing capabilities.}
\resumeItem{Implemented clean architecture patterns (MVC, service locator) using Zenject and UniRx in Unity.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6pt}
%-----------EDUCATION-----------


\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Southern Methodist University Guildhall, Texas, USA}{Aug 2024 -- May 2026}
{Master of Interactive Technology in Digital Game Development, Software Development
}{}

\resumeSubheading
{National Cheng Kung University, Tainan, Taiwan}{Sep 2017 -- Jun 2023}
{Bachelor of Architecture}

\resumeSubHeadingListEnd


% adjust vspace based on the space you want to leave between each section.
\end{document}